SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-24 scipy-1.0/paper.tex
dictionaries agree that performance-enhancing is hyphenated

Therefore, the relative abundance of different programming languages in the
SciPy library results from a combination of the usage of powerful performance
enhancing languages that interact well with Python (i.e., Cython), and the
usage of languages (and their libraries) that have proven reliable and
performant over many decades. The position that SciPy occupies near the
foundation of the scientific Python ecosystem is such that adoption of new
languages or major dependencies is generally unlikely---our choices are strongly
driven by long-term stability. GPU acceleration, new transpiling libraries, and
the latest JIT compilation approaches (i.e.,
Numba\cite{Lam:2015:NLP:2833157.2833162}) are very powerful, but currently fall
outside the remit of the main SciPy library. That said, we have recently
increased our efforts to support compatibility with some of these options, and
having our full test suite pass with the PyPy JIT
compiler\cite{Bolz:2009:TMP:1565824.1565827} is now a requirement in our
development workflow.

>>>>

Therefore, the relative abundance of different programming languages in the
SciPy library results from a combination of the usage of powerful performance-
enhancing languages that interact well with Python (i.e., Cython), and the
usage of languages (and their libraries) that have proven reliable and
performant over many decades. The position that SciPy occupies near the
foundation of the scientific Python ecosystem is such that adoption of new
languages or major dependencies is generally unlikely---our choices are strongly
driven by long-term stability. GPU acceleration, new transpiling libraries, and
the latest JIT compilation approaches (i.e.,
Numba\cite{Lam:2015:NLP:2833157.2833162}) are very powerful, but currently fall
outside the remit of the main SciPy library. That said, we have recently
increased our efforts to support compatibility with some of these options, and
having our full test suite pass with the PyPy JIT
compiler\cite{Bolz:2009:TMP:1565824.1565827} is now a requirement in our
development workflow.
